---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# VickyA4

<!-- badges: start -->
<!-- badges: end -->

**VickyA4** is a small R package that turns my Assignment 1–3 deliverables (PDFs and blog) into a **reproducible, structured corpus** for teaching and exploration.  
It ships with:

- A **tidy document-level dataset** `course_dataset` built from the PDFs under `inst/extdata/` (no external downloads).
- A **Shiny app** (under `inst/app/`) to interactively explore word counts, pages, estimated reading time, etc.
- A **pkgdown site** with function documentation and a getting-started vignette.

> Why a package for PDFs? Because reproducibility beats screenshots. The `data-raw/` pipeline converts static PDFs into a consistent, analysis-ready table that can be versioned, documented, and reused across assignments.

## Installation

You can install the development version of **VickyA4** from GitHub with:


```{r, eval = FALSE}
# install.packages("pak")
pak::pak("ETC5523-2025/assignment-4-packages-and-shiny-apps-Vicky-FengZ")
```


If you prefer `remotes`:

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("ETC5523-2025/assignment-4-packages-and-shiny-apps-Vicky-FengZ")
```


## Example

Load the package and inspect the bundled dataset:

```{r example}
library(VickyA4)

# A quick peek at the document-level corpus
head(corpus_docs)
```

Launch the Shiny app (this opens an interactive window; disabled while knitting the README):

```{r, eval = FALSE}
launch_app()
```

### What is inside `course_dataset`?

Each row is one PDF (one assignment). Columns include:

- `source`
- `n_paragraphs`, `n_words`, `n_chars`

You can compute simple summaries directly:

```{r}
summary(corpus_docs[c("n_paragraphs", "n_words", "n_chars")])
```

## Data provenance & reproducibility

- Source PDFs live **inside the package** under `inst/extdata/`.
- The dataset is built by **`data-raw/course_dataset.R`** using `pdftools`.  
  Rebuild locally with:

```{r}
# From the package root (development environment)
source("data-raw/build_corpus.R")
```

This design avoids brittle links and ensures anyone can reproduce the exact same dataset from the same PDFs.

## pkgdown

A pkgdown site will host function docs, the vignette, and examples.

- **Planned URL:** <https://YOUR-USERNAME.github.io/VickyA4/>
- After the first deployment, please update this README to link the live site.

## Limitations (and how to think critically)

- Text extracted from PDFs is not perfect: hyphenation, footers, or equations may affect counts.
- Sentence counts are approximate (punctuation-based). Treat `read_minutes_est` as a **guide**, not ground truth.
- If you need deeper NLP (topic modeling, readability indices), extend the `data-raw/` script and document the new fields.
