---
title: "getting-started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(VickyA4)
```

## Overview

This vignette shows how **VickyA4** transforms three assignment PDFs into a **reproducible corpus** and how to explore it:

1. PDFs are bundled under `inst/extdata/`.
2. `data-raw/course_dataset.R` extracts text and metadata (pages, words, sentences).
3. The result is stored as `course_dataset` (a tibble shipped with the package).
4. `launch_app()` opens a Shiny UI that helps users **reach similar conclusions** to the original analyses by interactively exploring the corpus (e.g., document length, estimated reading time, quick comparisons).

The goal is **traceability**: anyone can rebuild the same dataset from the same PDFs, and see how the interactive interface guides interpretation.

## The dataset

```{r}
# Print the full dataset
corpus_docs
```

**Columns (summary):**

- `source`: heuristic label (`"A1"`, `"A2"`, `"A3"`) and a human-readable label derived from the file name.
- `n_paragraphs`: paragraphs count from `pdftools::pdf_info()`.
- `n_words`: rough word count based on whitespace tokenization.
- `n_chars`: approximate character count via punctuation.

> Interpretation reminder: sentence detection is heuristic; treat `read_minutes_est` as indicative, not definitive.

## Quick exploration in R

You can answer simple questions without leaving R.

**Which assignment is the longest by word count?**

```{r}
corpus_docs[order(corpus_docs$n_words, decreasing = TRUE), 
               c("source","n_paragraphs", "n_words")]
```

**paragraphs vs words:**

```{r}
with(corpus_docs, data.frame(n_paragraphs, n_words))
```

## Launch the Shiny app

The app is bundled under `inst/app/` and **reads `course_dataset` directly** (no `read.csv()`):

```{r, eval = FALSE}
launch_app()
```

Inside the app you can:

- Select a document and read a concise summary (paragraphs, words, character).
- Toggle details like file path.
- Use the interface descriptions to understand what each field means and how to interpret the outputs.

This lightweight interactivity helps a user **replicate key takeaways** from the original assignments:
- Identify which deliverable is more substantial (length/complexity proxy).
- Benchmark reading effort for different pieces.
- Provide a consistent, transparent basis for comparison.

## Rebuilding the dataset (reproducibility)

To recreate `course_dataset` from the packaged PDFs:

```{r, eval = FALSE}
# From the package root (development setting)
source("data-raw/corpus_docs.R")
```

This will regenerate `data/course_dataset.rda`.  
If you add new PDFs to `inst/extdata/`, simply rerun the script; the corpus will update automatically.
